\epigraph{\textit{\enquote{ubuntu}\\\enquote{I am what I am because of who we all are.} (L. Gbowee definition)}}

Aaaaaand here I am, in the very last hour of thesis writing.
Here I'll thank all of you who made these four (and a half!) years a truly enriching experience.

In latitude order, Andrea and Daniel thanks for all the amazing moments in both the hemispheres!

The mosaicist who created the amazing artwork I used for the front cover, thanks!

Thanks to all my flatmates in Tarragona, each of you was amazing in a different way!

Thanks to all the Iberian hacktivists, activists, libertarians, political okupas, cooperativists, and social movement members: you are amazing. Just some names in random order: Diana, G10h4ck, Marc, Eva, Anna, Nuria, Gemma, Josep, Gianni, David, Viktor, Radikal, Bryan, Lluis, Dj Matusalem, Laia, Robi, Miguel, Marc, Aurora thanks! And some more: thanks to the whole LibreMesh community. Also thanks to all the people developing all the free\hyp{}as\hyp{}in\hyp{}free\hyp{}speech software I used for writing this thesis!

Thanks to all the people I had the chance to work with, I learnt a lot from you, both on the human and on the scientific point of view :D
Thanks to Tsung Yu, Ece, Santi, Cristina, Jonas, Dora, Eyyup, Gowri, Lydia, Lijun, Sarika, Georgiana, Daniel, Iker for all the good time!
Thanks to Jesús, Nuria, Werther (ciao Wertheer!!!), Maria for helping me with all the great scientific discussions!

Thanks to all the people that made hanging out in Tarragona and Barcelona a surprise every time: Michael, Micol, Stefano, Franzi, Giuliano, Irene, Barbara, Marcos, Laura, Luca, Raffaela, Antonella, Elena, Marc, Ivan, Iacopo I constantly missss you.

Thanks to Pilar and Vicenç for accepting me like one more in their family!

Thanks to my source of love, entropy, happiness, energy, and optimism for the future together: it looks shiny! You have no idea of how special your are, thanks Sofia!

Thanks to my supervisor Emilio Palomares, for supporting and trusting me so much, I hope you won't regret it!

Thanks to Sofia, Phil, Nuria, Maria, and Jesús for helping me with the correction of this thesis, it was most useful!

Thanks to Lannari Mannari all over the world and in Verona, just mentioning the kernel of it: Bruz and Cò $<3$ $<3$, Warrins, Skizzo, Dani, Lukez, Ghidappo, Tama, Stekkas, Sara looking forward to see you here or there!

Thanks to all the other amazing humans in Verona: Naar, Erica, Giulia, Pugliezza, Anteo, Ale, Kandels, and all the folk dancing people!

Thanks to my mother for always reminding me that job is far from being the most important thing in life and for taking care of all the mess I left behind in Verona (and for being amazing, you are).

Thanks to my Rosetta, Valentino, Teresa, Gianni, Maria Rosa, Giuseppe, Lucia for all the support over all this time!

Thanks to all the people who helped me to survive in London: Marche, Annalisa, Gianmaria, William, Francesco every excursion and every lunch or dinner I felt like at home, thanks, seriously.

Thanks to Phil, Mohammed, and Jun for being so amazing, each of you, I loved working, travelling, and hanging out with you! I hope to meet you as frequently as possible in the future!

Thanks to Piers RadioFrequency \cite{Calado2018} Barnes and to Jenny Nelson: all your curiosity, enthusiasm, honesty and ability to motivate students with a positive attitude is the best science can hope for!